Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-15 paper.tex
final edits to conclusions

The OpenMP code-generation built into \texttt{pyJac} is currently only capable of parallel execution, but extending this platform to shallow\slash deep-vectorizations (via \texttt{loo.py} and compiler \texttt{\#pragma}s) is a key priority going forwards as OpenMP is a standard library on most machines.
In addition, CUDA~\cite{Nvidia:2018} has been significantly more reliable in previous works~\cite{Niemeyer:2016aa,CurtisGPU:2017}, while Intel's open-source OpenCL alternative, ISPC~\cite{pharr2012ispc}, has been relatively stable and easy to work with during preliminary efforts with the unit-testing discussed in~\cref{s:unittest}.
The current deep-vectorization formulation would be executable for both CUDA and ISPC targets, as these languages implement double-precision atomic operations, further recommending their use.
It is also possible, particularly for the Intel OpenCL\slash POCL runtimes, that better performance\slash stability might be achieved using so-called ``explicit'' vectorization, i.e., through use of built-in vector types such as the \texttt{double8}; \add{specifically this change is hoped to enable vectorization on the POCL runtime} and might also enable deep-vectorization on the Intel OpenCL runtime.
The use of OpenCL Image\slash CUDA Texture memory to accelerate the indirect lookup for sparse matrix evaluation should be investigated as well.
Finally, future extensions of this work will include additional target languages (e.g., vectorized OpenMP, CUDA, ISPC) to improve ease of use and reliability, as well as improvements to the existing OpenCL targets, e.g., to enable meaningful deep-vectorized evaluation, \add{as well the implementation of reaction sorting~\cite{Sewerin20151375} to improve SIMD-efficiency (\cref{S:SIMD_scaling}).}

>>>>

The OpenMP code-generation built into \texttt{pyJac} is currently only capable of parallel execution, but extending this platform to shallow\slash deep-vectorizations (via \texttt{loo.py} and compiler \texttt{\#pragma}s) is a key priority going forwards since OpenMP is a standard library on most machines.
In addition, CUDA~\cite{Nvidia:2018} has been significantly more reliable in previous works~\cite{Niemeyer:2016aa,CurtisGPU:2017}, while Intel's open-source OpenCL alternative, ISPC~\cite{pharr2012ispc}, has been relatively stable and easy to work with during preliminary efforts with the unit-testing discussed in~\cref{s:unittest}.
The current deep-vectorization formulation would be executable for both CUDA and ISPC targets, as these languages implement double-precision atomic operations, further recommending their use.
It is also possible, particularly for the Intel OpenCL\slash POCL runtimes, that better performance\slash stability might be achieved using so-called ``explicit'' vectorization, i.e., through use of built-in vector types such as the \texttt{double8}. \add{Specifically, this change could enable vectorization on the POCL runtime} and might also enable deep vectorization on the Intel OpenCL runtime.
Using OpenCL Image\slash CUDA Texture memory to accelerate the indirect lookup for sparse matrix evaluation should be investigated as well.
Finally, future extensions of this work will include extending to additional target languages (e.g., vectorized OpenMP, CUDA, ISPC) to improve ease of use and reliability, improving the existing OpenCL targets (e.g., to enable meaningful deep-vectorized evaluation), \add{and implementing reaction sorting~\cite{Sewerin20151375} to improve SIMD efficiency (\cref{S:SIMD_scaling}).}
